Groundfish range shifts in response to climate: literature outline

### 2018-12-06 range-shift-lit-review-notes.Rmd
renaming

---
title: "Groundfish range shifts in response to climate: literature outline"
author: Philina English
date: "December 5, 2018"
bibliography: pbs-rangeshifts.bib
csl: apa-annotated-bibliograph-annotation-inline.csl 
output: pdf_document
---

>>>>

---
title: "Groundfish range shifts in response to climate: literature outline"
author: Philina English
date: "December 5, 2018"
bibliography: pbs-rangeshifts.bib
csl: apa-annotated-bibliograph-inline.csl 
output: html_document
---
